cardinalR: Generating interesting high-dimensional data structures

### 2025-05-06 paper-cardinalR.Rmd
Added gen_nonlinear

>>>>

The `gen_nonlinear(n, p, hc, non_fac)` function simulates a non-linear $2\text{-}D$ surface embedded in higher dimensions, constructed using inverse and trigonometric transformations applied to independent variables. 
The key geometry lies in dimensions 1–4, where:

* $X_1 \sim \mathcal{U}(0.1, 2)$: base variable (avoids zero to prevent division errors).
* $X_3 \sim \mathcal{U}(0.1, 0.8)$: independent auxiliary variable.
* $X_2 = \frac{hc}{X_1} + \text{non\_fac} \cdot \sin(X_1)$: non-linear combination of **hyperbolic and sinusoidal transformations**, creating sharp curvature and oscillation.
* $X_4 = \cos(\pi \cdot X_1) + \varepsilon$, with $\varepsilon \sim \mathcal{U}(-0.1, 0.1)$: additional nonlinear variation based on cosine, simulating more subtle periodic structure.

These transformations together result in a non-linear surface warped in multiple ways: sharp vertical shifts due to inverse terms, smooth waves from sine and cosine, and additional jitter.

If $p > 4$, the remaining dimensions are populated with Gaussian noise using `gen_noisedims()`:
